Changes in trip-making frequency by mode during the COVID-19 emergency: evidence from an online survey in Bangladesh

### 2020-10-23 Frequency-of-Travel-by-Mode-COVID-19-Bangladesh/Response-to-Reviewers-v2.Rmd

The paper presents an exploratory analysis of online survey results by 800 respondents on changes to their trip making behaviours by mode during the COVD pandemic. It is a well written paper, and I recommend publication. Some minor edits and adds are suggested below.

\textcolor{blue}{Thank you for your positive assessment and comments for improving the paper.}

- Figure 1: Please lengthen the y-axes for all figures, at the moment, it is a bit hard to read results off, because the axes are squashed.

\textcolor{blue}{Done. Hopefully the aspect of the figure will make it easier to read the results. Please also note that separate figures are generated for publication purposes, and these have better resolution.}

@@

- Table 1: Please mark whether the rows are before and columns are during in the cross tabulation. It would be a good idea to use something like a conditional colouring so that each cell value is coloured by the scale of the value, so that the patterns discussed come out visually clear. At the moment, one has to read the numbers carefully.

\textcolor{blue}{Rows and columns are now clearly labelled as "Before" and "During", respectively. We have also color-coded the cells by rows, to more easily see the patterns of change from before to during by mode and starting frequency.}

@@

- Otherwise, overall the paper is well written and the results are clearly discussed.

\textcolor{blue}{Thank you.}

- Bangladesh has very high density urban areas, it would be good to include a discussion on whether the online survey responses indicated which cities the respondents are from - what was the geography of the answers? While 800 is a decent number, the volume is still a small number when compared as a sample against full populations, further, different cities have different transit arrangements, and since the shared and transit modes seem most affected - a discussion of geography somewhere (which principal cities and their attributes) will enrich the discussion, and also as mentioned a discussion of the limitations of the sample size being still relatively small.

\textcolor{blue}{Thank you for this question, which echoes a question by Reviewer 2. We clarified this in the section 'Methods and Data'. The discussion in the revised paper provides additional information regarding the sample and its characteristics. In particular, the data set is a convenience sample which, while cannot be said to be representative of the population, is more homogeneous for younger, urban respondents. Convenience samples are used to address quickly emerging questions (see Fricker and Schonlau, 2002 in Field Methods, and Jager et al., 2017, in Monographs of the Society for Research in Child Development). Convenience samples have been used in COVID-19 research (for instance by Astroza et al., 2020, in Transport Findings) to generate knowledge in the context of a rapidly evolving public health situation. Bangladesh, in particular, is a challenging country to obtain probabilistic samples, due to a general reticence of the public, and in particular females, to provide information to unknown parties, as discussed in more detail in Jamal et al. (2020) in Transportation Research Part D, among other authors (also see Mitra, 2016). Hopefully the revised version does a better job of explaining the context and limitations of the study.}

\textcolor{blue}{Thank you again for your feedback, and we hope that the revisions will address your suggestions to your satisfaction.}

\textcolor{blue}{Mitra, Suman Kumar, 2016. Land Use, Land Value, and Transportation: Essays on Accessibility, Carless Households, and Long-Distance Travel. PhD thesis, University of California, Irvine.}

@@

# Reviewer 2

The level of reliability of the conclusions critically depends on the reliability of the sample, which is not analysed at all, i.e., there is no analysis of the level of representativeness of the sample relative to the Bangladesh population. A social media sample likely overrepresents high incomes, young age, etc. This must be scrutinized.

This is relevant because in the paper, from the title to the summary in the last paragraph, the authors claim they represent mobility changes in a developing country: Bangladesh, which has 160 million people (very small sample=800)

\textcolor{blue}{Thank you for this comment. You are right that this is a convenience sample, something that was not explicitly discussed in the original submission, but that we have clarified in the section 'Methods and Data' of the revised paper.}

\textcolor{blue}{Convenience samples have the advantage of being quick and cost-efficient and, despite their lower generalizability, when they are homogeneous they are useful to address rapidly emerging questions (see Fricker and Schonlau, 2002 in Field Methods, and Jager et al., 2017, in Monographs of the Society for Research in Child Development). As you suspected, this particular data set has an over-representation of the 16-30 years age group, whereas 37\% of the country's population belongs to this group. Also, 66\% of the respondents are male and 32\% are females compared to country's 49:51 male-female ratio. These characteristics of the sample are expected in terms of online surveys as young adults are more familiar with online platforms, especially in the context of a developing country context. Also, in the case of Bangladesh, collecting a representative sample remains difficult because of overall public reluctance to participate, with women's strong unwillingness to share their information to unknown parties in particular in face-to-face interviews (see Jamal et al., 2020 in Transportation Research Part D). Interestingly, compared to  Jamal et al. (2020), who had only 15\% of responses from females, the online survey used in the present research achieved greater penetration among women.}

\textcolor{blue}{Given these characteristics, the sample cannot be said to be a probabilistic random sample, but is rather homogeneous for urban, younger respondents, and has greater representation from females than comparable samples obtained from face-to-face interviews in Bangladesh. We would argue that the benefits of reporting the information while clearly noting the characteristics of the convenience sample outweigh the limitations (also see Astroza et al., 2020, in Transport Findings).}

@@

Other comments:

- No information of what contagion containment measures, if any, were in place during the time of the survey (e.g., lockdown, school closures)

\textcolor{blue}{Thanks for this comment. In the revised version we provide further information about this, and note that the country was under partial lock-down during the survey period, which meant that only essential services remained open, offices were running on rotation basis, all educational institutes were closed and public transport services were running at 50\% capacity.}

@@

\textcolor{blue}{Rows and columns are now clearly labelled as "Before" and "During", respectively. Also, we color-coded the cells by rows, after a comment by Reviewer 1.}

- Uber is not ridesharing, it is ridesourcing or ride-hailing.

\textcolor{blue}{This has been changed throughout the paper.}

\textcolor{blue}{Thank you again for your feedback, and we hope that the revisions will address your suggestions to your satisfaction. We believe that the paper has been improved as a result.}

### 2020-10-23 Frequency-of-Travel-by-Mode-COVID-19-Bangladesh/Frequency-of-Travel-by-Mode-COVID-19-Bangladesh.Rmd
v2 First version of revisions and response to reviewers for proof-reading

---
title: Changes in trip-making frequency by mode during the COVID-19 emergency in Bangladesh
author:
  - name: Shaila Jamal
    email: jamals16@mcmaster.ca
    affiliation: McMaster University
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
    footnote: 1
address:
  - code: McMaster University
    address: School of Earth, Environment and Society, McMaster University, Hamilton, ON, L8S 4K1, Canada
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
 The COVID-19 pandemic has had a profound impact on mobility in every country and region around the world. Recent studies help to illuminate some of the dimensions of change - however, the evidence is still scant in developing countries. The objective of this paper is to present an exploratory analysis of the changes in the frequency of trip-making by mode during the COVID-19 emergency in Bangladesh. The results confirm an overall loss of mobility in the form of reduced trip-making frequency by all modes, but the changes are not uniform across modes. In particular, there was a greater loss of mobility for bus, rickshaw, and CNG auto-rickshaw, and some adoption of walking during the pandemic.

@@

The objective of this paper is to investigate changes in the trip-making frequency by different modes of transportation during the COVID-19 emergency in Bangladesh. Using data from a recent survey that asked respondents to report mobility levels before and during the pandemic, we pose the following questions:

@@

Data used for this paper come from an online survey, "Exploring the potential of travel mode change behavior in the post-lock-down and post-pandemic (COVID-19) period" conducted during July - August 2020 in Bangladesh. The country was under partial lock-down during the survey period where essential services remained open, offices were running on rotation basis, all educational institutes were closed and public transport services were running at 50% capacity. The survey was disseminated through various electronic means along with a widespread social media campaign and promotion in various social media sites and groups. In addition to socio-economic and demographic information of the respondents, the survey covered different aspects of travel such as travel behavior before and during COVID-19, knowledge related to COVID-19, and opinions and perceptions regarding travel behavior after lock-down and post-pandemic situation.

For the purpose of this paper, we use two questions that provide information about trip-making frequency by eight modes of transportation. The modes are **car**, **ride-hailing** (e.g., Uber, Pathao), **rickshaw**, **CNG auto-rickshaw** (a rickshaw-like vehicle powered by compressed natural gas), **bus**, motorcycle/scooter (hereafter just **motorcycle**), **walking**, and **bicycle** (there was an additional catch-all category **other** which we ignore here). Participants in the survey used the following levels to report their frequency of traveling by each mode both before and during COVID-19: _Never_, _Rarely_, _Once a week_, _2-3 trips per week_, _4-5 trips per week_, _Almost daily_. There are $n=800$ responses in the data set.

@@

The findings reported here provide important changes in mobility in a developing country during COVID-19. In general there was a loss of mobility across-the-board, but modes that require interaction with strangers (ride-hailing, bus, rickshaw, and CNG auto-rickshaw) were more affected. Travel by car, motorcycle, and bicycle were somewhat less affected, and there is evidence of some adoption of walking during the pandemic.

>>>>

---
title: "Changes in trip-making frequency by mode during the COVID-19 emergency: evidence from an online survey in Bangladesh"
author:
  - name: Shaila Jamal
    email: jamals16@mcmaster.ca
    affiliation: McMaster University
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
    footnote: 1
address:
  - code: McMaster University
    address: School of Earth, Environment and Society, McMaster University, Hamilton, ON, L8S 4K1, Canada
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
 The COVID-19 pandemic has had a profound impact on mobility in every country and region around the world. Recent studies help to illuminate some of the dimensions of change - however, the evidence is still scant in developing countries. The objective of this paper is to present an exploratory analysis of the changes in the frequency of trip-making by mode during the COVID-19 emergency in Bangladesh. The analysis is based on an online sample conducted during the pandemic, and the results confirm an overall loss of mobility, especially among younger people, in the form of reduced trip-making frequency by all modes. In addition, the results suggest that changes are not uniform across modes, and in particular the loss of mobility was more pronounced for bus, rickshaw, and CNG auto-rickshaw. In contrast, there was some adoption of walking during the pandemic.

@@

The objective of this paper is to investigate changes in the trip-making frequency by different modes of transportation during the COVID-19 emergency in Bangladesh. Using data from a recent online survey that asked respondents to report mobility levels before and during the pandemic, we pose the following questions:

@@

Data used for this paper come from an online survey, "Exploring the potential of travel mode change behavior in the post-lock-down and post-pandemic (COVID-19) period", conducted during July - August 2020 in Bangladesh ($n=800$). The survey was disseminated through various electronic means along with a widespread social media campaign and promotion in various social media sites and groups. In addition to the respondents' socio-demographic information, the survey covered different aspects of travel such as travel behavior before and during COVID-19, knowledge related to COVID-19, and opinions and perceptions regarding travel behavior after lock-down and post-pandemic situation.

Like other surveys conducted during COVID-19 [e.g., @Astroza2020mobility], this is a convenience sample. Convenience samples have the advantage of being quick and cost-efficient and, despite their lower generalizability, when they are homogeneous they are useful to address rapidly emerging questions [Fricker2002advantages; @Jager2017convenience]. This particular data set has an over-representation of the 16-30 years age group, whereas 37% of the country's population belongs to this group [@Bangladesh2015]. Also, 66% of the respondents are male and 32% are females compared to country's 49:51 male-female ratio [@Bangladesh2015]. These characteristics of the sample are expected in terms of online surveys as young adults are more familiar with online platforms, especially in the context of a developing country context. Also, in the case of Bangladesh, collecting a representative sample remains difficult because of overall public reluctance to participate, with women's strong unwillingness to share their information to unknown parties in particular in face-to-face interviews [see @Jamal2020perceptions]. In fact, compared to  Jamal et al. [-@Jamal2020perceptions; Table 1], who had only 15% of responses from females, the online survey used in the present research achieved greater penetration among women.

In terms of geography, respondents were asked to identify the name of the district they reside. The resulting sample has 48% of respondents who live in Dhaka. Although, there are some differences in availability of transportation services between cities, especially between Dhaka and cities outside Dhaka, the mode use frequency indicates that only 15% never used buses and 32% never used ride-hailing services before COVID-19, which means these modes were available to most of the respondents and a vast majority has used them to some extent before the lock-down.

Given the above characteristics, the sample cannot be said to be a probabilistic random sample, but is rather homogeneous for urban, younger respondents, and has greater representation from females than comparable samples obtained from face-to-face interviews in Bangladesh.

The context for the study was the country-wide emergency situation during COVID-19, with required physical distancing recommendations and relevant health regulations in place. Bangladesh was under partial lock-down during the survey period, with only essential services open, offices running on a rotation basis, all educational institutes closed, and public transport services running at 50% capacity. For the purpose of this paper, we use two questions that provide information about trip-making frequency by eight modes of transportation. The modes are **car**, **ride-hailing** (e.g., Uber, Pathao), **rickshaw**, **CNG auto-rickshaw** (a rickshaw-like vehicle powered by compressed natural gas), **bus**, motorcycle/scooter (hereafter just **motorcycle**), **walking**, and **bicycle** (there was an additional catch-all category **other** which we ignore here). Participants in the survey used the following levels to report their frequency of traveling by each mode both before and during COVID-19: _Never_, _Rarely_, _Once a week_, _2-3 trips per week_, _4-5 trips per week_, _Almost daily_.

@@

The findings reported here suggest important changes in mobility in a developing country during COVID-19, which (given the characteristics of the convenience sample) may be more representative of younger, urban residents in Bangladesh. In general there was a loss of mobility across-the-board, but modes that require interaction with strangers (ride-hailing, bus, rickshaw, and CNG auto-rickshaw) were more affected. Travel by car, motorcycle, and bicycle were somewhat less affected, and there is evidence of some adoption of walking during the pandemic.

### 2020-10-23 Frequency-of-Travel-by-Mode-COVID-19-Bangladesh/Frequency-of-Travel-by-Mode-COVID-19-Bangladesh.tex
v2 First version of revisions and response to reviewers for proof-reading

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Changes in trip-making frequency by mode during the COVID-19 emergency in Bangladesh},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{Changes in trip-making frequency by mode during the COVID-19 emergency
in Bangladesh}
    \author[McMaster University]{Shaila Jamal}
   \ead{jamals16@mcmaster.ca} 
    \author[McMaster University]{Antonio Paez\corref{1}}
   \ead{paezha@mcmaster.ca} 
      \address[McMaster University]{School of Earth, Environment and Society, McMaster University, Hamilton,
ON, L8S 4K1, Canada}
      \cortext[1]{Corresponding Author}

  \begin{abstract}
  The COVID-19 pandemic has had a profound impact on mobility in every
  country and region around the world. Recent helps to illuminate some of
  the dimensions of change - however, the evidence is still scant in
  developing countries. The objective of this paper is to present an
  exploratory analysis of the changes in the frequency of trip-making by
  mode during the COVID-19 emergency in Bangladesh. The results confirm an
  overall loss of mobility in the form of reduced trip-making frequency by
  all modes, but the changes are not uniform across modes. In particular,
  there was a greater loss of mobility for bus, rickshaw, and CNG
  auto-rickshaw, and some adoption of walking during the pandemic.
  \end{abstract}

@@

Data used for this paper come from an online survey, ``Exploring the
potential of travel mode change behavior in the post-lock-down and
post-pandemic (COVID-19) period'' conducted during July - August 2020 in
Bangladesh. The survey was available both in Bengali and English and
disseminated through various electronic means along with a widespread
social media campaign and promotion in various social media sites and
groups. In addition to socio-economic and demographic information of the
respondents, the survey covered different aspects of travel such as
travel behavior before and during COVID-19, knowledge related to
COVID-19, and opinions and perceptions regarding travel behavior after
lock-down and post-pandemic situation.

For the purpose of this paper, we use two questions that provide
information about trip-making frequency by eight modes of
transportation. The modes are \textbf{car}, \textbf{ride-hailing} (e.g.,
Uber, Pathao), \textbf{rickshaw}, \textbf{CNG auto-rickshaw} (a
rickshaw-like vehicle powered by compressed natural gas), \textbf{bus},
motorcycle/scooter (hereafter just \textbf{motorcycle}),
\textbf{walking}, and \textbf{bicycle} (there was an additional
catch-all category \textbf{other} which we ignore here). Participants in
the survey used the following levels to report their frequency of
traveling by each mode both before and during COVID-19: \emph{Never},
\emph{Rarely}, \emph{Once a week}, \emph{2-3 trips per week}, \emph{4-5
trips per week}, \emph{Almost daily}. There are \(n=800\) responses in
the data set.

@@

@@

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\usepackage{graphicx}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Changes in trip-making frequency by mode during the COVID-19 emergency: evidence from an online survey in Bangladesh},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{Changes in trip-making frequency by mode during the COVID-19 emergency:
evidence from an online survey in Bangladesh}
    \author[McMaster University]{Shaila Jamal}
   \ead{jamals16@mcmaster.ca} 
    \author[McMaster University]{Antonio Paez\corref{1}}
   \ead{paezha@mcmaster.ca} 
      \address[McMaster University]{School of Earth, Environment and Society, McMaster University, Hamilton,
ON, L8S 4K1, Canada}
      \cortext[1]{Corresponding Author}

  \begin{abstract}
  The COVID-19 pandemic has had a profound impact on mobility in every
  country and region around the world. Recent studies help to illuminate
  some of the dimensions of change - however, the evidence is still scant
  in developing countries. The objective of this paper is to present an
  exploratory analysis of the changes in the frequency of trip-making by
  mode during the COVID-19 emergency in Bangladesh. The analysis is based
  on an online sample conducted during the pandemic, and the results
  confirm an overall loss of mobility, especially among younger people, in
  the form of reduced trip-making frequency by all modes. In addition, the
  results suggest that changes are not uniform across modes, and in
  particular the loss of mobility was more pronounced for bus, rickshaw,
  and CNG auto-rickshaw. In contrast, there was some adoption of walking
  during the pandemic.
  \end{abstract}

@@

Data used for this paper come from an online survey, ``Exploring the
potential of travel mode change behavior in the post-lock-down and
post-pandemic (COVID-19) period'', conducted during July - August 2020
in Bangladesh (\(n=800\)). The survey was disseminated through various
electronic means along with a widespread social media campaign and
promotion in various social media sites and groups. In addition to the
respondents' socio-demographic information, the survey covered different
aspects of travel such as travel behavior before and during COVID-19,
knowledge related to COVID-19, and opinions and perceptions regarding
travel behavior after lock-down and post-pandemic situation.

Like other surveys conducted during COVID-19 (e.g., Astroza et al.,
2020), this is a convenience sample. Convenience samples have the
advantage of being quick and cost-efficient and, despite their lower
generalizability, when they are homogeneous they are useful to address
rapidly emerging questions (Fricker2002advantages; Jager et al., 2017).
This particular data set has an over-representation of the 16-30 years
age group, whereas 37\% of the country's population belongs to this
group (Bangladesh Bureau of Statistics, 2015). Also, 66\% of the
respondents are male and 32\% are females compared to country's 49:51
male-female ratio (Bangladesh Bureau of Statistics, 2015). These
characteristics of the sample are expected in terms of online surveys as
young adults are more familiar with online platforms, especially in the
context of a developing country context. Also, in the case of
Bangladesh, collecting a representative sample remains difficult because
of overall public reluctance to participate, with women's strong
unwillingness to share their information to unknown parties in
particular in face-to-face interviews (see Jamal et al., 2020). In fact,
compared to Jamal et al.~{[}(2020); Table 1{]}, who had only 15\% of
responses from females, the online survey used in the present research
achieved greater penetration among women.

In terms of geography, respondents were asked to identify the name of
the district they reside. The resulting sample has 48\% of respondents
who live in Dhaka. Although, there are some differences in availability
of transportation services between cities, especially between Dhaka and
cities outside Dhaka, the mode use frequency indicates that only 15\%
never used buses and 32\% never used ride-hailing services before
COVID-19, which means these modes were available to most of the
respondents and a vast majority has used them to some extent before the
lock-down.

Given the above characteristics, the sample cannot be said to be a
probabilistic random sample, but is rather homogeneous for urban,
younger respondents, and has greater representation from females than
comparable samples obtained from face-to-face interviews in Bangladesh.

The context for the study was the country-wide emergency situation
during COVID-19, with required physical distancing recommendations and
relevant health regulations in place. Bangladesh was under partial
lock-down during the survey period, with only essential services open,
offices running on a rotation basis, all educational institutes closed,
and public transport services running at 50\% capacity. For the purpose
of this paper, we use two questions that provide information about
trip-making frequency by eight modes of transportation. The modes are
\textbf{car}, \textbf{ride-hailing} (e.g., Uber, Pathao),
\textbf{rickshaw}, \textbf{CNG auto-rickshaw} (a rickshaw-like vehicle
powered by compressed natural gas), \textbf{bus}, motorcycle/scooter
(hereafter just \textbf{motorcycle}), \textbf{walking}, and
\textbf{bicycle} (there was an additional catch-all category
\textbf{other} which we ignore here). Participants in the survey used
the following levels to report their frequency of traveling by each mode
both before and during COVID-19: \emph{Never}, \emph{Rarely}, \emph{Once
a week}, \emph{2-3 trips per week}, \emph{4-5 trips per week},
\emph{Almost daily}.

@@

\leavevmode\hypertarget{ref-Bangladesh2015}{}%
Bangladesh Bureau of Statistics, 2015. Population monograph of
bangladesh. Age-sex composition of bangladesh population.

@@

\leavevmode\hypertarget{ref-Jager2017convenience}{}%
Jager, J., Putnick, D.L., Bornstein, M.H., 2017. II. MORE than just
convenient: THE scientific merits of homogeneous convenience samples.
Monographs of the Society for Research in Child Development 82, 13--30.
doi:\href{https://doi.org/10.1111/mono.12296}{10.1111/mono.12296}

\leavevmode\hypertarget{ref-Jamal2020perceptions}{}%
Jamal, S., Mohiuddin, H., Paez, A., 2020. How do the perceptions of
neighborhood conditions impact active transportation? A study in
rajshahi, bangladesh. Transportation Research Part D: Transport and
Environment 87, 102525.
